### 2022-11-29 intro.Rnw
added paper 4

How can we know if a finding from a scientific study is really true? For
example, how can we know if the protective effect of a vaccine found in a study
is real? The answer to this question is of highest importance to scientists and
decision makers, but typically we can never know for sure as any study result
comes with uncertainty.

@@

In the midst of this doomsday, % , particularly from the hard-hit
% field of psychology,
various reforms were implemented to safe the reputation of science and to
prevent an escalation of the situation \citep[for an overview see
\eg{}][]{Munafo2017}. For instance, many journals adopted the ``registered
report'' format \citep{Chambers2021} in which a study proposal is peer reviewed
\emph{before} the study is conducted, and which, if accepted, gives provisional
publication acceptance regardless of the study outcome. Similarly, digital
infrastructure platforms, such as zenodo (\url{https://zenodo.org/}) or the open
science framework (\url{https://osf.io/}), were created to facilitate
preregistration, preprints, and code and data sharing, all of which have
substantially increased over the last decade \citep{Kidwell2016, Nosek2018,
  Rawlinson2019}. The practice of conducting replication studies has also gained
popularity, and several academic journals and funders are now explicitly
promoting and funding replication research \citep{NWO2016, NSL2018, Nature2022}.
Figure~\ref{fig:scholar} illustrates this trend via the yearly number of results
for ``\Sexpr{searchTerm}'' on Google Scholar over the last three decades. We see
that the numbers have been rapidly growing, especially after the mid 2000s (with
a minor drop in 2021, perhaps because of research slowing down due to the
COVID-19 pandemic).

@@

\begin{table}[!htb]
  \centering
  \caption{Study level summary statistics for an original and a replication
    study. The cumulative distribution function of the standard normal
    distribution is denoted by $\Phi(\cdot)$, and the $1 - \alpha$ quantile of
    the standard normal distribution is denoted by
    $\Phi^{-1}(1 - \alpha) = \z{\alpha}$. Confidence intervals and $p$-values
    are based on the normality assumption.}
  \label{tab:meta}
  \begin{tabular}{lcc}
    \toprule
    & Original study & Replication study \\
    \midrule
    effect estimate & $\that_o$ & $\that_{r}$ \\
    standard error & $\sigma_{o}$ & $\sigma_{r}$ \\
    $(1 - \alpha)$ confidence interval &
    $[\that_{o} \pm \z{\alpha/2} \sigma_{o}]$ &
    $[\that_{r} \pm \z{\alpha/2} \sigma_{r}]$ \\
    % $[\that_{o} - \z{\alpha/2} \sigma_{o}, \that_{o} + \z{\alpha/2} \sigma_{o}]$ &
    % $[\that_{r} - \z{\alpha/2} \sigma_{r}, \that_{r} + \z{\alpha/2} \sigma_{r}]$ \\
    $z$-value & $z_{o} = \that_{o}/\sigma_{o}$ & $z_{r} = \that_{r}/\sigma_{r}$ \\
    $p$-value (two-sided) & $p_{o} = 2\{1 - \Phi(|z_{o}|)\}$ & $p_{r} = 2\{1 - \Phi(|z_{r}|)\}$ \\
    % One-sided $p$-value & $p_{o} = 1 - \Phi(|z_{o}|)$ & $p_{r} = 2\{1 - \Phi(|z_{r}|)\}$ \\
    \bottomrule
  \end{tabular}
\end{table}

Most methods for analyzing replication studies can be formulated in terms of
study level summary statistics as shown in Table~\ref{tab:meta}. % Effect
% estimates, standard error, confidence intervals, and $p$-values
All of these are routinely reported in researcher articles, and if one of them
is missing they typically can, under some assumptions, be calculated from the
others. Using summary statistics is also often the only possible way for
conducting the analysis as the raw data from the original study may not be
available to the replicators. The most important statistic is the effect
estimate $\that$. It provides an estimate of the underlying effect size $\theta$
which quantifies the effect or association of an intervention/exposure with an
outcome variable. Typical effect sizes are mean differences and correlations
(for continuous outcomes), odds ratios (for binary outcomes), or hazard ratios
(for time to event outcomes). Depending on the type of effect size, a
transformation might be required so that the assumption of approximately
normally distributed effect estimates around the unknown effect size $\theta$
(for large enough sample sizes) is justified. This could be, for instance, the
Fisher $z$-transformation for correlations, or the log-transformation for
odds/hazard ratios \citep[chapter 11]{Cooper2019}. The associated standard error
$\sigma$ represents the statistical uncertainty of the estimate. Under the
assumption of (asymptotic) normality, confidence intervals for $\theta$ and
$p$-values for testing the null hypothesis $H_{0} \colon \theta = 0$ can be
computed as shown in Table~\ref{tab:meta}.

@@

The remaining criteria in Table~\ref{tab:rsdef} put more emphasis on
compatibility in effect size between the original and the replication study. For
example, the relative effect estimate $d = \that_{r}/\that_{o}$ quantifies how
much the replication effect estimate changed compared to the original, and the
smaller $d$ is the smaller the degree of replication success. Some projects also
report a confidence interval for $d$ \citep{Camerer2016, Camerer2018}, while
others ignore its uncertainty and make a binary cut at $d_{\text{min}} = 1$ to
define replication success \citep{Errington2021}. In contrast, the criteria
based on confidence and prediction intervals define effect size compatibility on
an absolute scale. However, the criterion based on the original confidence
interval ignores the uncertainty from the replication, whereas the criterion
based on the replication confidence interval ignores the uncertainty from the
original study. The prediction interval criterion, on the other hand, takes into
account both sources of uncertainty \citep{Patil2016}. Yet, declaring
``replication success'' based on the prediction interval may be logically
questionable due to its connection to the meta-analytic $Q$-test.
% as it may also be seen as an instance of the ``absence of evidence fallacy''
% \citep{Altman1995};
That is, if the $p$-value from the $Q$-test is larger than $\alpha$ this is
equivalent to the replication effect estimate $\that_{r}$ being contained in its
$(1- \alpha)$ prediction interval. The null hypothesis of this test is defined
that the underlying effect sizes of original and replication study are the same
($H_{0} \colon \theta_{o} = \theta_{r}$), so a rejection of this null hypothesis
corresponds to demonstrating replication failure and not replication success.
Interpreting a failure to reject the null hypothesis as evidence for it is again
an instance of the ``absence of evidence fallacy''
\citep{Hedges2019}. % To establish replication success a
% test based on the null hypothesis $H_{0} \colon \theta_{o} \neq \theta_{r}$
% would be required \citep{Hedges2019}.
As in the case of defining replication success by simultaneous non-significance
of original and replication study, the mismatch of the null hypothesis of the
prediction interval criterion results in the undesirable property that
``replication success'' can almost always be achieved if the sample size of the
studies is small enough as the prediction interval becomes wider with larger
standard errors.

@@

\begin{landscape}
\begin{table}
  \centering
  \caption{Subset of results from the Reproducibility Project: Cancer Biology
    \citep{Errington2021}. (P, X, E) denotes effect E from experiment X, from
    original paper P. Shown are original $\that_{o}$, replication $\that_{r}$,
    and pooled effect estimate $\that_{m}$ with 95\% confidence intervals,
    variance ratio $c = \sigma^{2}_{o}/\sigma^{2}_{r}$, relative effect estimate
    $d = \that_{r}/\that_{o}$, original $p$-value $p_{o}$, replication $p$-value
    $p_{r}$, meta-analytic $p$-value $p_{m}$, $Q$-test $p$-value $p_{Q}$, and
    sceptical $p$-value $p_{\mathrm{S}}$. A level $\alpha = 5\%$ is used as
    threshold for replication success via $p$-values, and a threshold
    $d_{\text{min}} = 1$ for the relative effect estimate.}
  \label{tab:RPCB}
% \resizebox{1\textwidth}{!}{%
<< "RPCB-table2", results = "asis" >>=
## select a subset with one effect per paper
set.seed(7)
rpcbTable <- rpcb |>
    na.omit() |>
    filter(smdo < 80, smdr < 80) |>
    group_by(paper) |>
    sample_n(size = 1) |>
    ungroup() |>
    arrange(pr2) |>
    select(id, smdoFormat, ## so,
           smdrFormat, smdmFormat,
           c, dFormat, ## sr,
           po2Format, pr2Format, pm2Format, pQFormat, ps2Format
           )

@@

\subsection{Reverse-Bayes assessment of replication studies}
In response to the lack of a standard criterion for replication success, various
methods have been proposed \citep[among others]{Verhagen2014, Simonsohn2015,
  Anderson2016, Patil2016, Johnson2016, Etz2016, vanAert2017, Ly2018, Harms2019,
  Hedges2019, Mathur2020, Held2020, Pawel2020, Bonett2020}. The focus of this
thesis is to refine and extended the proposal from \citet{Held2020} which
combines \emph{reverse-Bayes inference} and \emph{Bayesian model criticism} in a
method for assessing replication success. In the following, I will summarize its
main ideas and technical underpinnings.

@@

Bayesian inference is an approach to statistical inference where Bayes' theorem
is used to make probability statements about unknown parameters based on the
observed data. The central quantity for doing so is the distribution of the
parameters conditional on the data, called the \emph{posterior distribution}. It
can be obtained from Bayes' theorem
\begin{align*}
  f(\theta \given \text{data})
  = f(\theta) \times \frac{f(\text{data} \given \theta)}{f(\text{data})}
\end{align*}
meaning that the \emph{prior distribution} for the parameter $\theta$ with
density/probability mass function $f(\theta)$ is multiplied by the (normalized)
likelihood of the data, also know as \emph{Bayesian updating}. Parameter values
which increase the likelihood of the data become more likely \emph{a
  posteriori}, however, they are also weighted by their plausibility \emph{a
  priori} through the prior. As such, Bayesian inference provides a formal way
for combining information from the data at hand with external knowledge encoded
in the prior.

However, many also consider the prior to be the weak point of Bayesian
inference, as it is unclear how it should be specified in the absence of
external knowledge. The \emph{reverse-Bayes} approach, first proposed by
\citet{Good1950}, is one way of dealing with this issue. The idea is to reverse
Bayes' theorem
\begin{align*}
  f(\theta) = f(\theta \given \text{data}) \times
  \frac{f(\text{data})}{f(\text{data} \given \theta)}
\end{align*}
and instead ``downdate'' a posterior with the observed data. So, in contrast to
the conventional ``forward-Bayes'' approach where we start with a prior, update
it with the data, and end up with a posterior, the reverse-Bayes approach starts
with the posterior and ends up with the prior. Reverse-Bayes inference then
revolves around the question of whether the resulting prior is plausible in
light of external knowledge, and if so, this could be seen as support for the
specified posterior.

@@

Based on these observations, Box proposed two general approaches for conducting
Bayesian model criticism. First, the predictive density of the observed data (or
the value of a ``checking function'' applied to the observed data) can be
compared to its reference distribution via a \emph{prior predictive $p$-value}
\begin{align}
  p_{\text{Box}}
  = \Pr\left\{f(\text{data} \given \text{M}) <
  f(\text{observed data} \given \text{M})\right\},
  \label{eq:pppval}
\end{align}
that is, the probability of obtaining data with lower predictive density (``more
surprising'' data) than the observed data. The lower the $p$-value
$p_{\text{Box}}$, the more incompatibility between the observed data and the
assumed model M. This approach was used by \citet{Held2020}, and it will soon
be explained in more detail.
% The literature on Bayesian model criticism following \citet{Box1980} also
% mostly focused on prior predictive $p$-values. However, what has been mostly
% ignored is that Box also mentioned an alternative approach.
However, Box also mentioned a second approach which has mostly been forgotten.
If a second ``benchmarking'' model $\text{M}_{2}$ alternative to the model under
investigation $\text{M}_{1}$ is available, Box proposed that the \emph{prior
  predictive ratio}
\begin{align*}
  \text{PR}_{\text{Box}}
  = \frac{f(\text{observed data} \given \text{M}_{1})}{f(\text{observed data} \given \text{M}_{2})},
\end{align*}
the ratio of predictive densities from the observed data under both models,
could be used to judge the relative adequacy of model $\text{M}_{1}$. Again, the
lower the predictive ratio $\text{PR}_{\text{Box}}$, the less compatible the
observed data with the model $\text{M}_{1}$. Bayesian model criticism approaches
based on predictive ratios will be used in later parts of this
thesis.\footnote{Some readers may have noted that the predictive ratio is also
  the Bayes factor \citep{Jeffreys1961, Good1958} contrasting model
  $\text{M}_{1}$ to $\text{M}_{2}$. The prior predictive ratio model criticism
  approach is therefore particularly useful in combination with reverse-Bayes
  procedures based on Bayes factors, as will be demonstrated in later parts of
  this thesis (paper I and III).}

@@

This concludes the introduction to replication studies and the summary of the
reverse-Bayes assessment of replication success. Some additional properties
(\eg{} the null distribution of the sceptical $p$-value) and extensions (\eg{} a
one-sided version of the sceptical $p$-value, power and sample size
calculations) can be found in the original article by \citet{Held2020}. However,
the parts of the procedure that are relevant for this thesis have been
presented.

\subsubsection{Data and software}
The CC-By 4.0 licensed data from the Reproducibility Project: Cancer Biology
\citep{Errington2021} were downloaded from
\url{https://doi.org/10.17605/osf.io/e5nvr}. The relevant variables were then
extracted from the file ``\texttt{RP\_CB Final Analysis - Effect level
  data.csv}''. Code and data to reproduce the analyses and recompile the thesis
are available at \url{https://doi.org/10.5281/zenodo.XXXXXXX}. All analyses were
conducted in the R programming language version
\Sexpr{paste(version$major, version$minor, sep = ".")} \citep{R}. The packages
\texttt{dplyr} \citep{Wickham2022}, \texttt{ggplot2} \citep{Wickham2016},
\texttt{knitr} \citep{Xie2022}, \texttt{ReplicationSuccess} \citep{Held2020},
\texttt{UpSetR} \citep{Gehlenborg2019}, and \texttt{xtable} \citep{Dahl2019}
were used.

\newpage
\section{Open questions and thesis contributions}
\label{sec:summary}
\raggedbottom

This thesis consists of six papers. Paper I and II (and to a lesser extent III)
focus on extending the reverse-Bayes assessment of replication success from
\citet{Held2020}. Paper III presents a general Bayesian framework for
replication study design. Paper IV is a review paper about reverse-Bayes
methodology. Paper V is a short comment on another article which proposed a
reverse-Bayes method. Paper VI lists and illustrates questionable research
practices in simulation studies.

@@

@@

@@

The first authorship of this manuscript is shared with L. Kook. I had the idea
to invent a ``mock-method'' and use questionable research practices that make it
seem superior, to draw attention to the low standards in methodological
research. I then wrote a first draft of the manuscript and proposed the idea to
L. Kook and K. Reeve. L. Kook and myself then came up with the method ``AINET''
and started writing the simulation protocol. L. Kook took lead in developing the
R package \texttt{ainet} (\url{https://github.com/LucasKook/ainet}) and
simulation study code. K. Reeve provided feedback on the simulation protocol and
helped polishing the manuscript. Recently, I was invited to present the results
from this project at the CEN (Central European Network) conference 2023 in
Basel.

% Bibliography
\bibliographystyle{apalikedoiurl}
\bibliography{bibliography}

>>>>

How can we know if a finding from a scientific study is really true? For
example, how can we know if the protective effect of a vaccine found in a study
is real? The answer to such questions is of highest importance to scientists and
decision makers, but typically we can never know for sure as any study result
comes with uncertainty.

@@

In the midst of this doomsday, % , particularly from the hard-hit
% field of psychology,
various reforms were implemented to safe the reputation of science and to
prevent an escalation of the situation \citep[for an overview see
\eg{}][]{Munafo2017}. For instance, many journals adopted the ``registered
report'' format \citep{Chambers2021} in which a study proposal is peer reviewed
\emph{before} the study is conducted, and which, if accepted, gives provisional
publication acceptance regardless of the study outcome. Similarly, digital
infrastructure platforms, such as Zenodo (\url{https://zenodo.org/}) or the Open
Science Framework (\url{https://osf.io/}), were created to facilitate
preregistration, preprints, and code and data sharing, all of which have
substantially increased over the last decade \citep{Kidwell2016, Nosek2018,
  Rawlinson2019}. The practice of conducting replication studies has also gained
popularity, and several academic journals and funders are now explicitly
promoting and funding replication research \citep{NWO2016, NSL2018, Nature2022}.
Figure~\ref{fig:scholar} illustrates this trend via the yearly number of results
for ``\Sexpr{searchTerm}'' on Google Scholar over the last three decades. We see
that the numbers have been rapidly growing, especially after the mid 2000s (with
a minor drop in 2021, perhaps because of research slowing down due to the
COVID-19 pandemic).

@@

\begin{table}[!htb]
  \centering
  \caption{Study-level summary statistics for an original and a replication
    study. The cumulative distribution function of the standard normal
    distribution is denoted by $\Phi(\cdot)$, and the $1 - \alpha$ quantile of
    the standard normal distribution is denoted by
    $\Phi^{-1}(1 - \alpha) = \z{\alpha}$. Confidence intervals and $p$-values
    are based on the normality assumption.}
  \label{tab:meta}
  \begin{tabular}{lcc}
    \toprule
    & Original study & Replication study \\
    \midrule
    effect estimate & $\that_o$ & $\that_{r}$ \\
    standard error & $\sigma_{o}$ & $\sigma_{r}$ \\
    $(1 - \alpha)$ confidence interval &
    $[\that_{o} \pm \z{\alpha/2} \sigma_{o}]$ &
    $[\that_{r} \pm \z{\alpha/2} \sigma_{r}]$ \\
    % $[\that_{o} - \z{\alpha/2} \sigma_{o}, \that_{o} + \z{\alpha/2} \sigma_{o}]$ &
    % $[\that_{r} - \z{\alpha/2} \sigma_{r}, \that_{r} + \z{\alpha/2} \sigma_{r}]$ \\
    $z$-value & $z_{o} = \that_{o}/\sigma_{o}$ & $z_{r} = \that_{r}/\sigma_{r}$ \\
    $p$-value (two-sided) & $p_{o} = 2\{1 - \Phi(|z_{o}|)\}$ & $p_{r} = 2\{1 - \Phi(|z_{r}|)\}$ \\
    % One-sided $p$-value & $p_{o} = 1 - \Phi(|z_{o}|)$ & $p_{r} = 2\{1 - \Phi(|z_{r}|)\}$ \\
    \bottomrule
  \end{tabular}
\end{table}

Most methods for analyzing replication studies can be formulated in terms of
study-level summary statistics as shown in Table~\ref{tab:meta}. % Effect
% estimates, standard error, confidence intervals, and $p$-values
All of these are routinely reported in researcher articles, and if one of them
is missing they typically can, under some assumptions, be calculated from the
others. Using summary statistics is also often the only possible way for
conducting the replication success analysis as the raw data from the original
study may not be available to the replicators. The most important statistic is
the effect estimate $\that$. It provides an estimate of the underlying effect
size $\theta$ which quantifies the effect or association of an
intervention/exposure with an outcome variable. Typical effect sizes are mean
differences and correlations (for continuous outcomes), odds ratios (for binary
outcomes), or hazard ratios (for time to event outcomes). Depending on the type
of effect size, a transformation might be required so that the assumption of
approximately normally distributed effect estimates around the unknown effect
size $\theta$ (for large enough sample sizes) is justified. This could be, for
instance, the Fisher $z$-transformation for correlations, or the
log-transformation for odds/hazard ratios \citep[chapter 11]{Cooper2019}. The
associated standard error $\sigma$ represents the statistical uncertainty of the
estimate. Under the assumption of (asymptotic) normality, confidence intervals
for $\theta$ and $p$-values for testing the null hypothesis
$H_{0} \colon \theta = 0$ can be computed as shown in Table~\ref{tab:meta}.

@@

The remaining criteria in Table~\ref{tab:rsdef} put more emphasis on
compatibility in effect size between the original and the replication study. For
example, the relative effect estimate $d = \that_{r}/\that_{o}$ quantifies how
much the replication effect estimate changed compared to the original, and the
smaller $d$ is the smaller the degree of replication success. Some projects also
report a confidence interval for $d$ \citep{Camerer2016, Camerer2018}, while
others ignore its uncertainty and make a binary cut at $d_{\text{min}} = 1$ to
define replication success \citep{Errington2021}. The criteria based on
confidence and prediction intervals define effect size compatibility on an
absolute scale. However, the criterion based on the original confidence interval
ignores the uncertainty from the replication, whereas the criterion based on the
replication confidence interval ignores the uncertainty from the original study.
The prediction interval criterion takes into account both sources of uncertainty
\citep{Patil2016}. Yet, declaring ``replication success'' based on the
prediction interval may be logically questionable due to its connection to the
meta-analytic $Q$-test.
% as it may also be seen as an instance of the ``absence of evidence fallacy''
% \citep{Altman1995};
That is, if the $p$-value from the $Q$-test is larger than $\alpha$ this is
equivalent to the replication effect estimate $\that_{r}$ being contained in its
$(1- \alpha)$ prediction interval. The null hypothesis of this test is defined
that the underlying effect sizes of original and replication study are the same
($H_{0} \colon \theta_{o} = \theta_{r}$), so a rejection of this null hypothesis
corresponds to demonstrating replication failure and not replication success.
Interpreting a failure to reject the null hypothesis as evidence for it is again
an instance of the ``absence of evidence fallacy''
\citep{Hedges2019}. % To establish replication success a
% test based on the null hypothesis $H_{0} \colon \theta_{o} \neq \theta_{r}$
% would be required \citep{Hedges2019}.
As in the case of defining replication success by simultaneous non-significance
of original and replication study, the mismatch of the null hypothesis of the
prediction interval criterion results in the undesirable property that
``replication success'' can almost always be achieved if the sample size of the
studies is small enough as the prediction interval becomes wider with larger
standard errors.

@@

\begin{landscape}
\begin{table}
  \centering
  \caption{Subset of results from the Reproducibility Project: Cancer Biology
    \citep{Errington2021}. (P, X, E) denotes effect number E from experiment
    number X, from original paper number P. Shown are original $\that_{o}$,
    replication $\that_{r}$, and pooled effect estimate $\that_{m}$ with 95\%
    confidence intervals, variance ratio $c = \sigma^{2}_{o}/\sigma^{2}_{r}$,
    relative effect estimate $d = \that_{r}/\that_{o}$, original $p$-value
    $p_{o}$, replication $p$-value $p_{r}$, meta-analytic $p$-value $p_{m}$,
    $Q$-test $p$-value $p_{Q}$, and sceptical $p$-value $p_{\mathrm{S}}$. A
    level $\alpha = 5\%$ is used as threshold for replication success via
    $p$-values, and a threshold $d_{\text{min}} = 1$ for the relative effect
    estimate.}
  \label{tab:RPCB}
% \resizebox{1\textwidth}{!}{%
<< "RPCB-table2", results = "asis" >>=
## select a subset with one effect per paper
set.seed(7)
rpcbTable <- rpcb |>
    na.omit() |>
    filter(smdo < 80, smdr < 80) |>
    group_by(paper) |>
    sample_n(size = 1) |>
    ungroup() |>
    arrange(pr2) |>
    select(id, smdoFormat, ## so,
           smdrFormat, smdmFormat,
           c, dFormat, ## sr,
           po2Format, pr2Format, pm2Format, pQFormat, ps2Format
           )

@@

\subsection{Reverse-Bayes assessment of replication studies}
In response to the lack of a standard criterion for replication success, various
methods have been proposed \citep[among others]{Verhagen2014, Simonsohn2015,
  Anderson2016, Patil2016, Johnson2016, Etz2016, vanAert2017, Ly2018, Harms2019,
  Hedges2019, Mathur2020, Held2020, Pawel2020, Bonett2020}. The focus of this
thesis is to refine and extend the proposal from \citet{Held2020} which combines
\emph{reverse-Bayes inference} and \emph{Bayesian model criticism} in a method
for assessing replication success. In the following, I will summarize its main
ideas and technical underpinnings.

@@

Bayesian inference is an approach to statistical inference where Bayes' theorem
is used to make probability statements about unknown parameters based on the
observed data. The central quantity for doing so is the distribution of the
parameters conditional on the data, called the \emph{posterior distribution}. It
can be obtained from Bayes' theorem
\begin{align*}
  f(\theta \given \text{data})
  = f(\theta) \times \frac{f(\text{data} \given \theta)}{f(\text{data})}
\end{align*}
meaning that the \emph{prior distribution} for the parameter $\theta$ with
density/probability mass function $f(\theta)$ is multiplied by the (normalized)
likelihood of the data, also know as \emph{Bayesian updating}. Parameter values
which increase the likelihood of the data become more likely \emph{a posteriori}
but they are also weighted by their \emph{a priori} plausibility through the
prior. As such, Bayesian inference provides a formal way for combining
information from the data at hand with external knowledge encoded in the prior.

Many consider the prior to be also the weak point of Bayesian inference since it
is unclear how it should be specified in the absence of external knowledge. The
\emph{reverse-Bayes} approach, first proposed by \citet{Good1950}, is one way of
dealing with this issue. The idea is to reverse Bayes' theorem
\begin{align*}
  f(\theta) = f(\theta \given \text{data}) \times
  \frac{f(\text{data})}{f(\text{data} \given \theta)}
\end{align*}
and instead ``downdate'' a posterior with the observed data. So, in contrast to
the conventional ``forward-Bayes'' approach where we start with a prior, update
it with the data, and end up with a posterior, the reverse-Bayes approach starts
with the posterior and ends up with the prior. Reverse-Bayes inference then
revolves around the question of whether the resulting prior is plausible in
light of external knowledge, and if so, this could be seen as support for the
specified posterior.

@@

Based on these observations, Box proposed two general approaches for conducting
Bayesian model criticism. First, the predictive density of the observed data (or
the value of a ``checking function'' applied to the observed data) can be
compared to its reference distribution via a \emph{prior predictive $p$-value}
\begin{align}
  p_{\text{Box}}
  = \Pr\left\{f(\text{data} \given \text{M}) <
  f(\text{observed data} \given \text{M})\right\},
  \label{eq:pppval}
\end{align}
that is, the probability of obtaining data with lower predictive density (``more
surprising'' data) than the observed data. The lower the $p$-value
$p_{\text{Box}}$, the more incompatibility between the observed data and the
assumed model M. This approach was used by \citet{Held2020}, and it will soon
be explained in more detail.
% The literature on Bayesian model criticism following \citet{Box1980} also
% mostly focused on prior predictive $p$-values. However, what has been mostly
% ignored is that Box also mentioned an alternative approach.
However, Box also mentioned a second approach which has mostly been forgotten.
If a second ``benchmarking'' model $\text{M}_{2}$ alternative to the model under
investigation $\text{M}_{1}$ is available, Box proposed that the \emph{prior
  predictive ratio}
\begin{align*}
  \text{PPR}_{\text{Box}}
  = \frac{f(\text{observed data} \given \text{M}_{1})}{f(\text{observed data} \given \text{M}_{2})},
\end{align*}
the ratio of predictive densities from the observed data under both models,
could be used to judge the relative adequacy of model $\text{M}_{1}$. Again, the
lower the prior predictive ratio $\text{PPR}_{\text{Box}}$, the less compatible
the observed data with the model $\text{M}_{1}$. Bayesian model criticism
approaches based on prior predictive ratios will be used in later parts of this
thesis.\footnote{Some readers may have noted that the prior predictive ratio is
  also the Bayes factor \citep{Jeffreys1961, Good1958} contrasting model
  $\text{M}_{1}$ to $\text{M}_{2}$. The prior predictive ratio model criticism
  approach is therefore particularly useful in combination with reverse-Bayes
  procedures based on Bayes factors, as will be demonstrated in later parts of
  this thesis (paper I and III).}

@@

This concludes the introduction to replication studies and the summary of the
reverse-Bayes assessment of replication success. Some additional properties
(\eg{} the null distribution of the sceptical $p$-value) and extensions (\eg{} a
one-sided version of the sceptical $p$-value, power and sample size
calculations) can be found in the original article by \citet{Held2020}. However,
the relevant parts of the procedure have been presented. In the following, I
will discuss open questions and how they are addressed in this thesis.

\section{Open questions and thesis contributions}
\label{sec:summary}
\raggedbottom

This thesis consists of six papers divided into three parts. The first part
(Paper I, II, and III) focuses on methodology for design and analysis of
replication studies. The second part (Paper IV and V) revolves around
reverse-Bayes methodology in general. Paper IV is a review paper about
reverse-Bayes methodology and Paper V is a short comment on another article
which proposed a reverse-Bayes method. The last part (Paper VI) is about
integrity issues methodological research with simulations
studies. % The article lists and illustrates questionable
% research practices in simulation studies, and gives recommendations how to avoid
% them.

\subsection{Design and analysis of replication studies}

@@

\subsection{Reverse-Bayes methodology}

@@

\subsection{Integrity in methodological research}

@@

The first authorship of this manuscript is shared with L. Kook. I had the idea
to invent a ``mock-method'' and use questionable research practices that make it
seem superior, to draw attention to the low standards in methodological
research. I then wrote a first draft of the manuscript and proposed the idea to
L. Kook and K. Reeve. L. Kook and myself then came up with the method ``AINET''
and started writing the simulation protocol. L. Kook took lead in developing the
R package \texttt{ainet} (\url{https://github.com/LucasKook/ainet}) and
simulation study code. Myself, L. Kook, and K. Reeve then designed the final
simulation study and wrote the manuscript together. Recently, I was invited to
present the results from this project at the CEN (Central European Network)
conference 2023 in Basel.

\phantomsection
\addcontentsline{toc}{section}{Data and software}
\section*{Data and software}
The CC-By 4.0 licensed data from the Reproducibility Project: Cancer Biology
\citep{Errington2021} were downloaded from
\url{https://doi.org/10.17605/osf.io/e5nvr}. The relevant variables were then
extracted from the file ``\texttt{RP\_CB Final Analysis - Effect level
  data.csv}''. All analyses from this chapter were conducted in the R
programming language version \Sexpr{paste(version$major, version$minor, sep =
  ".")} \citep{R}. The packages \texttt{dplyr} \citep{Wickham2022},
\texttt{ggplot2} \citep{Wickham2016}, \texttt{knitr} \citep{Xie2022},
\texttt{ReplicationSuccess} \citep{Held2020}, \texttt{UpSetR}
\citep{Gehlenborg2019}, and \texttt{xtable} \citep{Dahl2019} were used. Code and
data to reproduce this thesis are available at
\url{https://doi.org/10.5281/zenodo.XXXXXXX}.

% Bibliography
\nocite{Pawel2020b, Held2021, Pawel2022c,Held2021b, Pawel2022d, Pawel2022e}
\bibliographystyle{apalikedoiurl}
\bibliography{bibliography}
